Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-08 paper/paper.tex
interim

\paragraph*{A note on implicit and explicit memory.}
While Markov Processes are usually memoryless, it is mathematically feasible to incorporate the previous states of such model into the current state. This extension may partially account for implicit memory at the behavioral level, but may not explain the underlying neurobiological implementation or accommodate explicit memory. Implicit memory-based processing arises in our MDP account of DMN function in several different forms: successive updates of a) the action policy and the value function, both being products of the past, as well as b) the deep non-linear relationships within the hierarchical connections of biological neural networks. The brain's adaptive synaptic connections can be thought as deep neural networks affording an implicit form of information compression of life experience. Such memory traces are implicitly stored in the neural machinery and can be retrieve as a form of knowledge during simulation of action rather than accessed as a stored explicit representation \citep{pezzulo2011grounding}. c) The neural processes in the hippocampus can be seen as some type of MCMC sampling for memory recall, which can also be a basis for scene construction processes across time-scales \citep{schacter2007remembering,Axelrod2017}.

>>>>

\paragraph*{A note on implicit and explicit memory.}
While Markov Processes are usually memoryless, it is mathematically feasible to incorporate the previous states of such model into the current state. This extension may partially account for implicit memory at the behavioral level, but may not explain the underlying neurobiological implementation or accommodate explicit memory. Implicit memory-based processing arises in our MDP account of DMN function in several different forms: successive updates of a) the action policy and the value function, both being products of the past, as well as b) the deep non-linear relationships within the hierarchical connections of biological neural networks. The brain's adaptive synaptic connections can be thought as deep neural networks affording an implicit form of information compression of life experience. Such memory traces are stored in the neural machinery and can be implicitly retrieve as a form of knowledge during simulation of action rather than accessed as a stored explicit representation \citep{pezzulo2011grounding}. c) Certain neural processes in the hippocampus can be seen as some type of MCMC sampling for memory recall, which can also be a basis for mental imagery across time-scales \citep{schacter2007remembering,Axelrod2017}.
